Staged Abstract Interpreters

### 2018-04-13 paper/paper.tex
update

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

%% Title information
\title[Short Title]{Staged Abstract Interpreter}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Subtitle}                     %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

@@

\subsection{Syntax and Concrete Semantics}
Continuation-passing style (CPS) is a widely used intermediate representation in compilation and analysis for functional
languages.

\subsection{Abstract Semantics}

\subsection{Closure Generation}

\subsection{Staged Abstract CE Interpreter}

@@

Generalize the idea to staged CESK abstract machine for direct style (or ANF), 
which has fully power for instantiating different analyses. We need to show that
it not merely reproduces abstract compilation by staged computation.

Olivier Danvy shows the relation between small-step CEK machine and big-step
CEK machine by applying a lightweight fix-point promotion. And it is well-known
that a staged interpreter (big-step abstract machine) is a compiler. 
Then a nature question is to ask what is the relation of their abstract 
counterparts.

We may show: 1) staged small-step abstract interpreter (classical AAM),
2) staged big-step abstract interpreter (ADI), 3) staged small-step abstract
interpreter is equivalent to staging a fix-point promoted big-step abstract 
interpreter, 4) soundness after staging.

Question: 1) Pushdown analysis can be obtained if the abstract interpreter is
written in a definitional way. Does pushdown property still exists after 
staging? 2) Pushdown analysis can be complicated in a small-step setting 
\cite{vardoulakis2010cfa2, earl2012introspective, gilray2016pushdown}. 
The Pushdown for Free (P4F for short) \cite{gilray2016pushdown} is probably the most 
simple solution. What is the relation between a staged P4F and a staged 
abstract defintional interpreter?

(ADI in Racket: \url{https://github.com/plum-umd/ abstracting-definitional-interpreters/}).

\section{Improving Performance}

@@

\section{Modular Analysis for Free?}

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review,anonymous]{acmart}
\documentclass[sigplan,anonymous,review]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

%% Title information
\title[Short Title]{Staged Abstract Interpreters}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Fast and Compositional Whole-Program Analysis for Free}                     %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

\section{Background}

\subsection{Staged Interpreter}

@@

@@

\subsection{what not to do when writing an abstract interpreter for staging}

\section{Heterogeneous Staging}

Staging to GPU?

@@

\section{Compositional Analysis for Free}
